### 2015-07-13 drafts/tmpsolutions.tex
Move old dissertation draft out of the way

Using \SRL{} in some form, whether it is in the familiar end of
Bayesian Networks or in the relatively adventerous end of methods that
support cycles, is much more elaborate than the above strategy. I'm
quite convinced that I need to publish a paper on this topic as well,
and arguably, if I should focus at the dissertation as a whole rather
than the individual parts, it makes sense to develop this theory
first, and then derive the VoID extensions from that.

@@

The 3.~semester evaluation committee also critisized the lack of a
paper, and said that I should produce a paper, at least a draft before
the end of the year. If I embark on a study of \SRL{}, this would not
be possible.

>>>>

Using \SRL{} in some form, whether it is in the familiar end of
Bayesian Networks or in the relatively adventerous end of methods that
support cycles, is much more elaborate than the above strategy. I'm
quite convinced that I need to publish a paper on this topic as well,
and arguably, if I should focus at the dissertation as a whole rather
than the individual parts, it makes sense to develop this theory
first, and then derive the VoID extensions from that as well as more
complex results.

@@

The 3.~semester evaluation committee also critisized the lack of a
paper, and said that I should produce a paper, at least a draft before
the end of the year. If I embark on a study of \SRL{}, this would not
be possible. There is a risk that it will take more than a year to finish
a work on this, and then there is little to fall back on.
